---
title: "Publications"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 1
    #code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```

IMPORTANT: * is the corresponding author.


# My first author articles

Dong, X., Gao, C., Guo, C., Li, W., & Cui, L. (2020). Time course of attentional bias in social anxiety: The effects of spatial frequencies and individual threats. Psychophysiology, 57(9), e13617. https://doi.org/10.1111/psyp.13617 (SSCI, JCR Q1, IF 4.016)

Dong, X., Liu, J., Oei, T. P. S., Cui, L., & Xiao, J. (2019). A Cognitive Model of the Familial Transmission of Depression. Journal of Aggression, Maltreatment & Trauma, 28(10), 1232–1249. https://doi.org/10.1080/10926771.2018.1501456 (SSCI, JCR Q3, IF 2.059)

Dong, X., Du, X., & Qi, B. (2016). Conceptual Knowledge Influences Decision Making Differently in Individuals with High or Low Cognitive Flexibility: An ERP Study. PLOS ONE, 11(8), e0158875. https://doi.org/10.1371/journal.pone.0158875 (SCI, JCR Q2, IF 3.24)

# My corresponding author articles

Zhang, K., Du, X., & Dong, X*. (2018). The impact of social motivation and self-others on creative performance (in Chinese). Studies of psychology and behavior, 16(3), 414-420. http://www.xml-data.org/XYYXWYJ/html/2018/3/2018-3-414.htm (CSSCI)

# Other articles

Xia, L., Cui, L., Zhang, Q., Dong, X., & Shi, G. (2018). Mechanisms of attentional selection bias for threatening emotions of anger and disgust in individuals with high-trait anxiety. Neuroreport, 29(4), 291–300. https://doi.org/10.1097/WNR.0000000000000953

Zhang, S., Dong, X., & Cui, L. (2020). ERP evidence for emotional sensitivity in social anxiety. Journal of Affective Disorders. https://doi.org/10.1016/j.jad.2020.09.111




# Adding R stuff

So far this is just a blog where you can write in plain text and serve your writing to a webpage. One of the main purposes of this lab journal is to record your progress learning R. The reason I am asking you to use this process is because you can both make a website, and a lab journal, and learn R all in R-studio. This makes everything really convenient and in the sam place. 

So, let's say you are learning how to make a histogram in R. For example, maybe you want to sample 100 numbers from a normal distribution with mean = 0, and standard deviation =1, and then you want to plot a histogram. You can do this right here by using an r code block, like this:

```{r}
samples <- rnorm(100, mean=0, sd=1)
hist(samples)
```

When you knit this R Markdown document, you will see that the histogram is printed to the page, along with the R code. This document can be set up to hide the R code in the webpage, just delete the comment (hashtag), from the cold folding option in the yaml header up top. For purposes of letting yourself see the code, and me see the code, best to keep it the way that it is. You learn all of these things and more can be customized in each R code block.

# The big idea

Use this lab journal to record what you do in R. This way I will be able to see what you are doing and help you along the way. You will also be creating a repository of all the things you do. You can make posts about everything. Learning specific things in R (project unrelated), and doing things for the project that we will discuss at the beginning of the Fall semester. You can get started now by fiddling around with googling things, and trying stuff out in R. I've placed some helpful starting links in the links page on this website

# What can you do right now by yourself?

It's hard to learn programming when you don't have specific problems that you are trying to solve. Everything just seems abstract.

I wrote an [introductory programming book that introduces R](https://crumplab.github.io/programmingforpsych/), and gives some [concrete problems for you to solve](https://crumplab.github.io/programmingforpsych/programming-challenges-i-learning-the-fundamentals.html). 

To get the hang of journaling and solving the problems to learn programming, my suggestion is that you use this .Rmd file to solve the problems. It would look like this:

# Problem 1

Do simple math with numbers, addition, subtraction, multiplication, division

```{r}
1+2
2*5
5/3
(1+6+4)/5

```

# Problem 2

Put numbers into variables, do simple math on the variables

```{r}
a<-1
b<-2
a+b

d<-c(1,2,3)
e<-c(5,6,7)
d+e
d*e
d/e

```

# Problem 3

Write code that will place the numbers 1 to 100 separately into a variable using for loop. Then, again using the seq function.

```{r}
# for loop solution
# i becomes the number 1 to 100 at each step of the loop


a <- length(100) # make empty variable, set length to 100
for (i in 1:100){
  a[i] <-i #assigns the number in i, to the ith index of a
}

print(a)

# for loop solution #2

a<-c() #create empty variable using combine command
for (i in 1:100){
  a<-c(a,i) # keeps combining a with itself and the new number in i
}
print(a)

# seq solution
a <- seq(1,100,1) # look up help for seq using ?seq() in console
print(a)

```

# Replace this with problem 4

And keep going. Try to solve the problems with different scripts that provide the same solution. Good luck, Happy coding.
